---
title: "Dashboard Draft"
author: "Meutia"
format:
  dashboard:
    orientation: rows
    theme: default
    css: custom.css
server: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, include = TRUE, warning = FALSE, message = FALSE)
```

```{r include=FALSE, echo = FALSE}
#| label: libraries
#| context: setup
library(tidyverse)
library(ggplot2)
library(dplyr)
library(stringr)
library(lubridate)
library(cobalt)
library(compareGroups)
```

```{r include=FALSE, echo = FALSE}
#| label: data loading
data_raw <- read.csv('unsw_datathon_2025.csv')
View(data_raw)
```

# Home {scrolling="true"}

##

<h1><span style="color:#423A8E">Welcome to the Australian Hip Fracture Registry for Prince of Wales Hospital</span></h1>

This dashboard is a tool to benchmark hospital performance against the ACSQHC clinical quality indicators. <br>

## 

### Hospital Snapshot


<div class="kpi-cards">
  <div class="kpi-card" style="background-color:#FFC107;">
   Active Patients <br>`r nrow(data_raw)`
  </div>

  <div class="kpi-card" style="background-color:#DC3545;">
   Last Modified <br>`r format(Sys.time(), "%d %b %Y", tz="Australia/Sydney")` <br>`r format(Sys.time(), "%H:%M:%S", tz="Australia/Sydney")`
  </div>

  <div class="kpi-card" style="background-color:#198754;">
   2022 Records <br>`r nrow(data_raw)`
  </div>

  <div class="kpi-card" style="background-color:#0D6EFD;">
   All Records <br>`r nrow(data_raw)`
  </div>
</div>


<style>

.kpi-cards {
  display: grid;
  grid-template-columns: repeat(4, minmax(200px, 1fr)); /* 4 columns */
  gap: 0.75rem;
  margin: 1rem 0;
}

.kpi-card {
  min-height: 80px;
  border-radius: 1rem;
  padding: 0.75rem 1rem;
  text-align: center;
  font-weight: 600;
  font-size: 0.98rem;
  color: #fff;
  box-shadow: 0 4px 12px rgba(0,0,0,0.12);

  display: flex;
  flex-direction: column;
  justify-content: center;
  align-items: center;
}

/* Responsive: 2 columns on tablets, stack on phones */
@media (max-width: 992px) {
  .kpi-cards { grid-template-columns: repeat(2, minmax(220px, 1fr)); }
}
@media (max-width: 576px) {
  .kpi-cards { grid-template-columns: 1fr; }
}

</style>


##

### Hip Fracture Clinical Care Standard


::: {.row}
::: {.col-md-4}
::: {.card style="height:100%; text-align:center;"}
**QS 1**

[Care at presentation](#qs-1){.btn .btn-primary .btn-sm style="margin-bottom:10px;"}
:::
:::

::: {.col-md-4}
::: {.card style="height:100%; text-align:center;"}
**QS 2**

[Pain management](#qs-2){.btn .btn-primary .btn-sm style="margin-bottom:10px;"}
:::
:::

::: {.col-md-4}
::: {.card style="height:100%; text-align:center;"}
**QS 3**

[Orthogeriatric model of care](#qs-3){.btn .btn-primary .btn-sm style="margin-bottom:10px;"}
:::
:::


::: {.col-md-4}
::: {.card style="height:100%; text-align:center;"}
**QS 4**

[Timing of surgery](#qs-4){.btn .btn-primary .btn-sm style="margin-bottom:10px;"}
:::
:::

::: {.col-md-4}
::: {.card style="height:100%; text-align:center;"}
**QS 5**

[Mobilisation and weight bearing](#qs-5){.btn .btn-primary .btn-sm style="margin-bottom:10px;"}
:::
:::

::: {.col-md-4}
::: {.card style="height:100%; text-align:center;"}
**QS 6**

[Minimising risk of another fracture](#qs-6){.btn .btn-primary .btn-sm style="margin-bottom:10px;"}
:::
:::


::: {.col-md-4}
::: {.card style="height:100%; text-align:center;"}
**QS 7**

[Transition from hospital care](#qs-7){.btn .btn-primary .btn-sm style="margin-bottom:10px;"}
:::
:::


# QS 1 {#qs-1}

<h1><span style="color:#423A8E">Care at presentation</span></h1>

A person presenting to hospital with a suspected hip fracture receives care that is guided by timely assessment and management of medical conditions, including cognition, pain, nutritional status and frailty. Arrangements are made according to a locally endorsed hip fracture pathway.

# QS 2 {#qs-2}

<h1><span style="color:#423A8E">Pain management</span></h1>

A person with a hip fracture is assessed for pain at the time of presentation to the emergency department and regularly throughout their acute admission. Pain management includes appropriate multimodal analgesia and nerve blocks, unless contraindicated.

# QS 3 {#qs-3}

<h1><span style="color:#423A8E">Orthogeriatric model of care</span></h1>

A person with a hip fracture is offered treatment based on an orthogeriatric model of care as defined in the Australian and New Zealand Guideline for Hip Fracture Care. A coordinated multidisciplinary approach is used to identify and manage malnutrition, frailty, cognitive impairment and delirium.

# QS 4 {#qs-4}

<h1><span style="color:#423A8E">Timing of surgery</span></h1>

A person with a hip fracture receives surgery within 36 hours of their first presentation to hospital.

# QS 5 {#qs-5}

<h1><span style="color:#423A8E">Mobilisation and weight bearing</span></h1>

A person with a hip fracture is mobilised without restrictions on weight bearing, starting the day of, or the day after, surgery, and at least once a day thereafter, according to their clinical condition and agreed goals of care.

# QS 6 {#qs-6}

<h1><span style="color:#423A8E">Minimising risk of another fracture</span></h1>

Before a person leaves hospital after a hip fracture, they receive a falls and bone health assessment and management plan, with appropriate referral for secondary fracture prevention.

# QS 7 {#qs-7}

<h1><span style="color:#423A8E">Transition from hospital care</span></h1>

Before a person leaves hospital after a hip fracture, an individualised care plan is developed that describes their goals of care and ongoing care needs. This plan is developed in discussion with the person and their family or support people. The plan includes mobilisation activities and expected function post-injury, wound care, pain management, nutrition, fracture prevention strategies, changed or new medicines, and specific rehabilitation services and equipment. On discharge, the plan is provided to the person and communicated with their general practice and other ongoing clinicians and care providers.

